### 2019-07-03 papers/journal/intro.tex
Update on the fig 2 legend
Minor Updated suggested By Somya
Minor Updated suggested By Somya. Without a ref.

\noindent 
%A characteristic feature of eukaryotic cells is the presence of multiple internal membrane-bounded compartments. 
The cytoplasm of all eukaryotic cells is broken up into distinct membrane-bound locations known as organelles: the
nuclear membrane, endoplasmic reticulum (ER), Golgi apparatus, vacuoles and lysosomes are examples of these.
%These compartments exchange molecules amo\-ngst themselves in small membrane-bounded packets called vesicles~\cite{alberts2002molecular}. 
%
%%The molecular interaction network that controls the vesicle traffic system involves dozens of varieties of molecules that regulate the flow of cargo. 
%
%%Due to this, obtaining a complete understanding of the VTS through physical experimentation alone is a hard problem.
%
%%Highly reduced models of vesicle traffic have previously provided insight into how the chemical composition of various cellular compartments can emerge out of molecular regulation and cargo flow. 
%
%%However, the high complexity of problems in VTS restricts the use of traditional methods like simulation and statistical reasoning~\cite{mani2016stacking}. 
%The high complexity of problem restricts the use of traditional methods like simulation and statistical reasoning and the requirement of precise analysis makes formal methods an ideal candidate. 
%%In this paper, using formal methods, we solve the problem of completing incomplete VTS graphs while also considering constraints due to molecular interactions, thereby demonstrating the effectiveness of such methods.
%
%
Cargo is moved between these organelles in small membrane-bound
transporters known as vesicles \cite{stenmark2009rab}.
%
This organization resembles a transport logistics network, and is commonly known as the membrane traffic system.
%
Membrane traffic underpins nearly every aspect of eukaryotic cellular
physiology, including human cellular physiology.
%
Defects in membrane traffic lead to a variety of disorders or even
cell death \cite{stenmark2009rab}.
%
Understanding how membrane traffic functions is therefore one of the
central challenges of cell biology.
%

@@

Another interesting question is the completion of the VTS \cite{synthesisGupta}. 
%
The current picture of the VTS is far from complete; we do not yet know how many of the cellular proteins reach their resident compartments within the cell, and new vesicle routes are being discovered every year~\cite{nickel2018unconventional,weill2018toolbox}. 
%
Completing the VTS is a difficult task for many important reasons: 
\begin{enumerate}
	\item The core VTS is conserved across eukaryotes, the traffic network in different organisms \cite{richardson2015evolutionary, barlow2017seeing}, and even in different cell types within an organism can be different~\cite{stoops2014trafficking,zhou2015arp2}.
	\item Although the basic molecular machinery is the same for all vesicle fusion events, the details of regulation can be different~\cite{davletov2007regulation,di2010calcium}.
	\item Molecules can have redundant routes within the cell~\cite{shimizu2014compensatory,nakatsukasa2014nutrient}.
	\item Behaviour of traffic molecules in vitro is different from their behavior inside cells~\cite{furukawa2014multiple}. 
	\item It can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knockouts of traffic molecules \cite{hirst2004epsinr,mishev2013small}.
\end{enumerate}

@@

\par We have implemented the encoding in a flexible tool, which can handle both connectivity question and a wide range of synthesis queries. 
%
We have applied our synthesis tool on several VTSs including
two found-in-nature VTSs.
%
We manage to scale the tool to the size that makes the tool biologically relevant. 
%
Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research.
%

>>>>

\noindent 
%A characteristic feature of eukaryotic cells is the presence of multiple internal membrane-bounded compartments. 
Eukaryotic cells contain distinct membrane-bound objects known as organelles: endoplasmic reticulum (ER), Golgi apparatus, vacuoles and lysosomes are examples of these.
%These compartments exchange molecules amo\-ngst themselves in small membrane-bounded packets called vesicles~\cite{alberts2002molecular}. 
%
%%The molecular interaction network that controls the vesicle traffic system involves dozens of varieties of molecules that regulate the flow of cargo. 
%
%%Due to this, obtaining a complete understanding of the VTS through physical experimentation alone is a hard problem.
%
%%Highly reduced models of vesicle traffic have previously provided insight into how the chemical composition of various cellular compartments can emerge out of molecular regulation and cargo flow. 
%
%%However, the high complexity of problems in VTS restricts the use of traditional methods like simulation and statistical reasoning~\cite{mani2016stacking}. 
%The high complexity of problem restricts the use of traditional methods like simulation and statistical reasoning and the requirement of precise analysis makes formal methods an ideal candidate. 
%%In this paper, using formal methods, we solve the problem of completing incomplete VTS graphs while also considering constraints due to molecular interactions, thereby demonstrating the effectiveness of such methods.
%
%
Cargo is moved between these organelles in small membrane-bound
transporters known as vesicles \cite{stenmark2009rab}.
%
This organization resembles a transport logistics network, and is commonly known as the membrane traffic system.
%
Membrane traffic underpins nearly every aspect of eukaryotic cellular
physiology, including human cellular physiology.
%
Defects in membrane traffic lead to a variety of disorders or even
cell death \cite{stenmark2009rab}.
%
Understanding how membrane traffic functions is therefore one of the
central challenges of cell biology.
%

@@

Another interesting question is the completion of the VTS \cite{synthesisGupta}. 
%
The current picture of the VTS is far from complete; we do not yet know how many of the cellular proteins reach their resident compartments within the cell, and new vesicle routes are being discovered every year~\cite{nickel2018unconventional,weill2018toolbox}. 
%
Completing the VTS is a difficult task for many important reasons: 
\begin{enumerate}
	\item The core VTS is conserved across eukaryotes, the traffic network in different organisms \cite{richardson2015evolutionary, barlow2017seeing}, and even in different cell types within an organism can be different~\cite{stoops2014trafficking,zhou2015arp2}.
	\item Although the basic molecular machinery is the same for all vesicle fusion events, the details of regulation can be different~\cite{davletov2007regulation,di2010calcium}.
	\item Molecules can have redundant routes within the cell~\cite{shimizu2014compensatory,nakatsukasa2014nutrient}.
	\item Behaviour of traffic molecules in vitro is different from their behavior inside cells~\cite{furukawa2014multiple}. 
	\item It can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knockouts of traffic molecules \cite{hirst2004epsinr,mishev2013small}.
\end{enumerate}
        \item Lastly, interpreting experimental results can be difficult, since behaviour of traffic molecules in vitro is different from their behavior inside cells.

@@

\par We have implemented the encodings in a flexible tool, which can handle both connectivity question and a wide range of synthesis queries. 
%
We have applied our synthesis tool on several VTSs including
two found-in-nature VTSs.
%
We manage to scale the tool to the size that makes the tool biologically relevant. 
%
Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research.
%
